---
title: "Thoughts on Experimental Design and Reproducible Research"
author: "Sean Davis, MD, PhD<br/>Center for Cancer Research, National Cancer Institute<br>National Institutes of Health
<br/>https://twitter.com/seandavis12<br/>https://seandavi.github.io/"
subtitle: "A Guided Discussion"
date: "`r Sys.Date()`"
output: 
  ioslides_presentation:
    widescreen: TRUE
    df_print: kable
    smart: TRUE
bibliography: citations.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Scientific Method

## Deciding on an Experimental Question

## Ethical Considerations
Ethical considerations are integral to the initiation, conduct, and publication of experimental results.  In terms of experimental design, consider the following *3Rs* [@Fry2014-wu].

- Replacement

- Refinement

- Reduction

## Ethical Considerations

### Replacement
Does the experiment need to be performed at all or performed as envisioned?

- Literature review
    - Has the study already been done?
    - What designs have been used or proposed for similar experiments in the past?
- Are the experimental materials appropriate for the questions at hand?
    - Cell lines useful instead of animals
    - Low cost tech instead of high cost (PCR vs. Sequencing)

## Ethical Considerations

### Refinement
Does the experiment as envisioned gather appropriate data, have defined stopping rules, standard procedures, and clarity on sources of variability?

- Define important data to gather.
    - Dependent variables and independent variables may not be enough.
    - Consider confounders, technical details, ambient conditions, and metadata (date, time, machine, experimenter, etc.).
- Define when an experiment is "complete". 
- Establish standard procedures as clearly as possible.
- Define, to the extent possible, sources of variability and reliability in your approach.


## Overview

- Introductions
- Experimental Design
  
- Reproducible Computational Research Principles
- 



## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

# subtitle

Just a test.

## Slide with Plot

```{r pressure}
plot(pressure)
```

## References {.smaller}